### 2022-09-29 Thesis/text/ergebnisse.tex
pagerefs

The results show that the functional requirements (as defined in \ref{sec:Requirements}) are met in almost all cases. Fn$\_$req1 to fn$\_$req5 are all completely fulfilled. Fn$\_$req6 is only partly fulfilled as the test showed potential shortcomings of the implemented collision behavior. Fn$\_$req7 satisfies the acceptance criteria, but fn$\_$req8 is only partly met by the implemented behavior to find alternative goals. Finally, the battery behavior meets all acceptance criteria, and fn$\_$req9 is fulfilled.

>>>>

The results show that the functional requirements (as defined in \ref{sec:Requirements}) are met in almost all cases. Fn$\_$req1 to fn$\_$req5 are all completely fulfilled. Fn$\_$req6 is only partly fulfilled as the test showed potential shortcomings of the implemented collision behavior. Fn$\_$req7 satisfies the acceptance criteria, but fn$\_$req8 is only partly met by the implemented solution to find alternative goals. Finally, the battery behavior meets all acceptance criteria, and thus fn$\_$req9 is fulfilled.
